Modern BTree\\ techniques

### 2020-01-16 btree/presentation.tex
Hybrid index + bw tree

        \onslide<6>
        \begin{tikzpicture}[]
            \smallbtree{1}{2.5}{}{}{}{green-box}
            \smallbtree{2}{1}{left=4cm of node11, yshift=-0.6cm}{}{}{blue-box}
            \node[bloom-filter, above=0.5cm of node21, fill=redBad] (bloom) {};
            \node[arrow-pointer, left=0.5cm of nodebox2.west] (inserts) {\footnotesize{Insert}};
            \node[arrow-pointer, above=1.2cm of inserts] {\footnotesize{Read}};
            \draw[->, btree-line] (bloom.south) -- (nodebox2.north);
        \end{tikzpicture}

@@

@@

\end{frame}
\note{
    ClickHouse - B-Tries
}

>>>>

        \onslide<6>
        \begin{tikzpicture}[]
            \smallbtree{1}{2.5}{}{}{}{green-box}
            \smallbtree{2}{1}{left=4cm of node11, yshift=-0.6cm}{}{}{blue-box}
            \node[bloom-filter, above=0.5cm of node21, fill=redBad] (bloom) {};
            \node[arrow-pointer, left=0.5cm of nodebox2.west] {\footnotesize{Insert}};
            \draw[->, btree-line] ([yshift=-0.2cm]nodebox2.south)
                .. controls ([yshift=-2.5cm] nodebox2) and ([yshift=-2.5cm] nodebox1) ..
                ([yshift=-0.2cm]nodebox1.south);
        \end{tikzpicture}

        \onslide<7>
        \begin{tikzpicture}[]
            \smallbtree{1}{2.5}{}{}{}{green-box}
            \smallbtree{2}{1}{left=4cm of node11, yshift=-0.6cm}{}{}{blue-box}
            \node[bloom-filter, above=0.5cm of node21, fill=redBad] (bloom) {};
            \node[arrow-pointer, left=0.5cm of nodebox2.west] (inserts) {\footnotesize{Insert}};
            \node[arrow-pointer, above=1.2cm of inserts] {\footnotesize{Read}};

            \draw[->, btree-line] ([yshift=-0.2cm]nodebox2.south)
                .. controls ([yshift=-2.5cm] nodebox2) and ([yshift=-2.5cm] nodebox1) ..
                ([yshift=-0.2cm]nodebox1.south);
        \end{tikzpicture}

        \onslide<8>
        \begin{tikzpicture}[]
            \smallbtree{1}{2.5}{}{}{}{green-box}
            \smallbtree{2}{1}{left=4cm of node11, yshift=-0.6cm}{}{}{blue-box}
            \node[bloom-filter, above=0.5cm of node21, fill=redBad] (bloom) {};
            \node[arrow-pointer, left=0.5cm of nodebox2.west] (inserts) {\footnotesize{Insert}};
            \node[arrow-pointer, above=1.2cm of inserts] {\footnotesize{Read}};

            \draw[->, btree-line] ([yshift=-0.2cm]nodebox2.south)
                .. controls ([yshift=-2.5cm] nodebox2) and ([yshift=-2.5cm] nodebox1) ..
                ([yshift=-0.2cm]nodebox1.south);
            \draw[->, btree-line] (bloom.south) -- (nodebox2.north);
            \draw[->, btree-line] (bloom.east) -| (nodebox1.north);
        \end{tikzpicture}

@@

    \begin{center}
    \textbf{Bw-Tree}
    \vspace{1cm}

    \begin{overprint}[12cm]
        \onslide<1>
        \begin{tikzpicture}[]
            \node[btree-node] (node1) {};

            \draw[->, btree-line, color=white] (node1) -- (node2);
            \draw[->, btree-line, color=white] (node1) -- (node3);
            \draw[->, btree-line, color=white] (node1) -- (node4);

            \draw[->, btree-line, color=white] (node2) -- (node5);
            \draw[->, btree-line, color=white] (node2) -- (node6);

            \draw[->, btree-line, color=white] (node3) -- (node7);
            \draw[->, btree-line, color=white] (node3) -- (node8);

            \draw[->, btree-line, color=white] (node4) -- (node9);
            \draw[->, btree-line, color=white] (node4) -- (node10);

            \path
                node[draw, right=5cm of node1.east, minimum width=1.2cm] (header1) {\textbf{\normalsize{ID}}}
                node[draw, right=0 of header1, minimum width=1.2cm] (header2) {\textbf{\normalsize{PTR}}}
                    node[draw, below=0 of header1, minimum width=1.2cm] (row11) {\normalsize{1}}
                    node[draw, right=0 of row11, minimum width=1.2cm] (row12) {\normalsize{0x...}}
                    node[draw, below=0 of row11, minimum width=1.2cm] (row21) {\normalsize{2}}
                    node[draw, right=0 of row21, minimum width=1.2cm] (row22) {\normalsize{0x...}}
                    node[behind path, fit=(header1)(header2)(row11)(row12)(row21)(row22)] (mapping) {};

            \draw[->, btree-line] (row11.west)
            .. controls ([xshift=-1cm] row11) and ([yshift=2cm] node4) ..
            (node4.center);

            \draw[->, btree-line] (row21.west)
            .. controls ([xshift=-2cm] row21) and ([xshift=2cm] node8) ..
            (node8.center);

        \end{tikzpicture}
    \end{overprint}
    \end{center}
\end{frame}

    \begin{center}
    \only<1> {
        \textbf{Is that all?}
    }
    \only<2> {
        \includegraphics[width=0.5\textwidth,center]{nein.png}
    }
    \only<3> {
    }

@@

\end{frame}
\note{
    ClickHouse - B-Tries
    HyPer - ART
    MSFT Hekaton - Bw-Tree
    Redis, MemSQL - Skip list
    Silo - Masstree
}
